Current State of Knowledge Representation Systems for Robotics

### 2011-12-01 criteria.tex
Updated criteria following latest discussion with Michael

@@

	As an agent acting at human-like time scale and dealing with temporal
	concepts (like actions), a robot may want to represent, and possibly to
	reason, about time. Time representation is split into two distinct
	abilities: representing time points (both in the past -- which is roughly
	equivalent to assignment of timestamps to events the robot perceives -- and
	in the future), and representing \emph{passing time} (durations, timespans)
	like in \emph{``the eggs will be cooked in 10 min''}.

@@

	Linked to the context representation, but seen from another angle,
	knowledge representation systems may provide explicit ways to model other
	point of view on the world. This ability is often refered as the
	\emph{perspective taking} ability.

@@

        \item{\bf Introspection: knowledge about the knowledge}

@@

    \begin{itemize}
            \item{\bf Prediction and projection tasks}

        \begin{itemize}
            \item{\bf Projection task}: determining whether or not some condition while hold after a sequence of actions.
            \item{\bf Legality task}: determining whether a sequence of action can be performed starting in some initial state.
        \end{itemize}

        \item{\bf Reasoning in uncertainty}

        \item{\bf Presupposition accomodation}

        \emph{Presupposition accomodation} is the ability for the system to
        automatically create a context allowing to make sense of a proposition.[...]

>>>>

\section{Survey Inclusion criteria}

\begin{itemize}
\item  Run on \emph{service robot} (robots that interact with objects in a
semantic-rich environment),

\item  Ground their knowledge in the physical world (physically embedded),
\begin{itemize}
\item  Able to \emph{resolve entities}
\item  Able to automatically create new object instances
\end{itemize}

\item  Be able to merge different knowledge modalities,
\item  Be endowed with on-line, dynamic reasoning (not just a static
		dictionary)

@@

	[...] Time representation is split into two distinct
	abilities: representing time points (both in the past -- which is roughly
	equivalent to assignment of timestamps to events the robot perceives -- and
	in the future), and representing \emph{passing time} (durations, timespans)
	like in \emph{``the eggs will be cooked in 10 min''}.

    Mention here \emph{Chronicles}.

@@

	Linked to the context representation, but seen from another angle,
	knowledge representation systems may provide explicit ways to model other
	point of view on the world. This ability is often referred as the
	\emph{perspective taking} ability.

@@

        \item{\bf Introspection: What can I do?}
		\begin{itemize}
			\item{\bf General introspection}
			The ability for the robot to represent its own capabilities.
			\item{\bf Meta-cognition: knowledge about the knowledge}
		\end{itemize}

    \begin{itemize}

        \item{\bf Standard Reasoning Techniques}
		\begin{itemize}

			\item{\bf Inferences and backtracking}
			\item{\bf Classification}			
			\item{\bf Inconsistencies detection}

        \item{\bf Reasoning with uncertainty}

        \item{\bf Presupposition accommodation}

        \emph{Presupposition accommodation} is the ability for the system to
        automatically create a context allowing to make sense of a proposition.[...]

			\item{\bf Prediction and projection tasks}

		\begin{itemize}

		\item{\bf Projection task}: determining whether or not
		some condition while hold after a sequence of actions.

		\item{\bf Legality task}: determining whether a sequence of action can be
		performed starting in some initial state.

		\item{\bf Diagnosis}

		\item{\bf Planning}

@@

### 2011-12-01 krs-survey.tex
Updated criteria following latest discussion with Michael

@@

\subsubsection{Introspection: knowledge about the knowledge}
\label{sect|introspection}
Support for introspection?

\subsubsection{Modifying its knowledge}

In DL -> always possible to modify the ABox, not always possible to alter the TBox

@@

\subsubsection{Prediction and projection tasks}
\label{sect|prediction-projection}

\subsubsection{Reasoning in uncertainty}

@@

A knowledge representation system able to copte with presupposition
accomodation would be able to take into account this (usually under-defined)
information that is not grounded into perception for later inferences.

@@

Note also that presupposition accomodation implies a bidirectional link of the
symbolic knowledge model with a geometric (or physical) model of the
environment. This article focuses on symbolic knowledge representation systems,
but we shall mention when a KRS explicitely provides support for presupposition
accomodation.

@@

\subsubsection{The planning task}

@@

\subsection{Underlying knowledge model}

>>>>

\fxfatal{Discuss time chronicles~\cite{Ghallab1996}}

@@

\subsubsection{Introspection: what can I do?}
\label{sect|introspection}

\paragraph{General introspection}

Modelling of the robot capabilities.

\paragraph{Meta-cognition: knowledge on the knowledge}

Narrower, more technical dimension of the introspection.

@@

\subsubsection{Standard reasoning techniques}

Backtracking,...

\paragraph{Decidability}

...

\subsubsection{Reasoning with uncertainty}

@@

A knowledge representation system able to copte with presupposition
accommodation would be able to take into account this (usually under-defined)
information that is not grounded into perception for later inferences.

@@

Note also that presupposition accommodation implies a bidirectional link of the
symbolic knowledge model with a geometric (or physical) model of the
environment. This article focuses on symbolic knowledge representation systems,
but we shall mention when a KRS explicitly provides support for presupposition
accommodation.

\subsubsection{Prediction and projection and diagnosis tasks}
\label{sect|prediction-projection}

\paragraph{Diagnosis}: this corresponds to the ability to rewind on past events
in case of failure to provide possible explanation. This can be seen as the
temporal reverse of the projection task.

\subsubsection{Planning}
\label{sect|planning}

Making decision based on prediction

\subsubsection{Modifying the knowledge structure}

All systems allow to modify the ABox, not always possible to alter the TBox

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Underlying knowledge model}
